### 2018-11-25 Sections/optical_routers.tex
Touch up

The refractive index of an electro-optic medium\index{Electro-optic medium} is a function $n(E)$ of the applied electric field $E$. This function varies only slightly with $E$, such that using Taylor series expansion\index{Taylor series} about \mbox{$E=0$},
\begin{align}
n(E) = n+a_1E + \frac{1}{2}a_2E^2+\dots.
\end{align}

@@

Sound, or acoustic waves, are vibrations that travel through a medium with a velocity characteristic of the medium. This can create perturbations in the refractive index of the optical medium, thus modifying the velocity of light passing through the medium. Thus sound can be used to modify the effect of the medium on light. That is, sound can control the direction of propagation of light. This acousto-optic effect is used to make a variety of devices like optical modulators, switches, deflectors, filters, isolators, frequency shifters and spectrum analysers. This is shown in Fig.~\ref{fig:AOM}.

@@

In the presence of a static magnetic field, certain materials act as polarisation rotators, known as the Faraday effect\index{Faraday effect}. The angle of rotation is proportional to distance and the rotary power $\rho$ (angle per unit length), which is proportional to the component $B$ of the magnetic flux density in the direction of wave propagation,
\begin{align}
	\rho=VB,
\end{align}
where $V$ is known as the Verdet constant\index{Verdet constant}, which is a function of wavelength $\lambda_0$.

@@

A simple form of magneto-optic modulator consists of a parallel-sided disk of material placed in a small coil. An alternating current in the coil provides a magnetic field normal to the plane of the disk. The material becomes magnetised in this direction and light propagating through the disk undergoes a polarisation rotation about its plane of polarisation. The modulation of the angle of the plane of polarisation induced by the alternating current may be converted to amplitude modulation\index{Amplitude modulation} by subsequently passing the beam through a polariser.

>>>>

The refractive index of an electro-optic medium\index{Electro-optic medium} is a function $n(E)$ of the applied electric field $E$. This function varies only slightly with $E$, such that using a Taylor series expansion\index{Taylor series} about \mbox{$E=0$} we obtain,
\begin{align}
n(E) = n+a_1E + \frac{1}{2}a_2E^2+\dots.
\end{align}

@@

Sound, or acoustic waves\index{Acoustic waves}, are vibrations that travel through a medium with a velocity characteristic of the medium. This can create perturbations in the refractive index of the optical medium, thus modifying the velocity of light passing through the medium. Thus sound can be used to modify the effect of the medium on light. That is, sound can control the direction of propagation of light. This acousto-optic effect is used to make a variety of devices like optical modulators, switches, deflectors\index{Deflectors}, filters\index{Filters}, isolators\index{Isolators}, frequency shifters\index{Frequency shifters} and spectrum analysers\index{Spectrum analysers}. This is shown in Fig.~\ref{fig:AOM}.

@@

In the presence of a static magnetic field, certain materials act as polarisation rotators, known as the Faraday effect\index{Faraday effect}. The angle of rotation is proportional to distance and the rotary power\index{Rotary power} $\rho$ (angle per unit length), which is proportional to the component $B$ of the magnetic flux density in the direction of wave propagation,
\begin{align}
	\rho=VB,
\end{align}
where $V$ is known as the Verdet constant\index{Verdet constant}, which is a function of wavelength $\lambda_0$.

@@

A simple form of magneto-optic modulator comprises a parallel-sided disk of material placed in a small coil. An alternating current in the coil provides a magnetic field normal to the plane of the disk. The material becomes magnetised in this direction and light propagating through the disk undergoes a polarisation rotation about its plane of polarisation. The modulation of the angle of the plane of polarisation induced by the alternating current may be converted to amplitude modulation\index{Amplitude modulation} by subsequently passing the beam through a polariser.
